Gamification Effectiveness on Education

### 2024-04-16 paper/paper.qmd
added the data source section

@@

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

>>>>

This paper reproduces the result from @DEMARCOS2017155. This paper will provided a overview of the data used in that study. For more detailed explanation of the data please visit the original study(insert link).

@@

The results from pretest(@tb-pretest) are pretty such the same for each group which aligns with the fact that this study was given before the experiment began.
